Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-10-03 forgerard.tex
forging ahead

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k$, and
$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the infrequent selection of supernovae
heavily extinguished by host-galaxy dust.
Outliers  are also clearly distinguished in  $EW_{Ca}$--$\lambda_{Si}$ space.

@@

\subsection{Two Extrinsic Parameters}
\color{red}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
\color{black}
None of the 20000 links of 
our Monte Carlo chains for $\delta$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k$ and $k_1$  on supernova magnitudes
with probability $(1-5\times 10^{-5})$.

\color{red}
Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k + \gamma^1_X k_1$
and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
estimate $R_V=A_V/(E(B-V)-zeropoint$ per supernova.  These values are shown in Figure~\ref{avebv:fig}.

@@

Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\end{equation}
The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
the results shown here vary only at the percent level when making this approximation.
Similarly our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
\end{equation}

In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
in directions
$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.16 & 2.82 \\
0.74 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
onto the Fitzpatrick plane
have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/avebv_synth.pdf}
    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
onto the Fitzpatrick plane.}
   \label{avebv:fig}}
\end{figure}

The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
I will contemplate whether this could mean anything.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/avrv_synth.pdf}
    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
   \label{avrv:fig}}
\end{figure}

The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
external dust is responsible for most of our $k$ and $D$ parameters.

@@

\textcolor{red}{
The values of $\delta_X/\delta_V$, plotted in  Figure~\ref{deltaratio:fig}, are not monotonic with color: they increase from the $U$ to $V$, and then decrease
from $V$ to $I$,
a consequence
of which is that
a reddening in $B-V$ comes with a blueing in $V-R$.
Also apparent is that a reddening of $B-V$ is associated with a brightening of the supernova.
The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$ are shown in Figure~\ref{rx:fig}.
Although the posteriors of $\delta$ are close to Gaussian, $\delta_B-\delta_V$ can approach zero, resulting in the
elongated tail in negative  $R_{\delta X}$.
All values are significantly negative.}
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
more complicated underlying supernova physics.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/deltaratio.pdf}
   \caption{68\% credible intervals of $\frac{\delta_X}{\delta_V}$ at the effective wavelengths of the corresponding bands.
   \label{deltaratio:fig}}
\end{figure}

@@

\section{Supernova Model Part 2}
\label{model2:sec}
We hypothesize that at peak brightness
SN~Ia broadband magnitudes and colors are correlated with
spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
broadband colors.
Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
of intrinsic variation is accommodated.
The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
\textcolor{red}{The intrinsic magnitudes are then
modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}

We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature}:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on an
extrinsic-color parameter $k$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma$ are the slopes that connect the extrinsic-color
parameter and observed magnitudes.

To constrain the degrees of freedom and degeneracies inherent in the model we impose that
\color{red}
each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
conditions break the 
degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\color{black} 
\begin{equation}
\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \langle D \rangle=0, \gamma^0_{0} > 0, \gamma^1_{0} < 0, \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$
\color{red}
(when running our fits, $k$ and $D$ are set to
identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ distinguishes the two.)
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other, as is apparent after 
running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
with relatively broad credible intervals and lower maximum likelihood.
\color{black}
As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.

\section{SN 2014J in the Context of Our Model}
\label{sn2014j:sec}

Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
These data are fit to the model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma_X}{\gamma_V}-1\right)k +  \left(\frac{\delta_X}{\delta_V}-1\right)D,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.

The best-fit parameters for SN~2014J are 
%----
$k= 2.67$, $ D=-1.63$ with covariance
%----
\begin{equation}
\begin{pmatrix}
0.047 & 0.044 \\
0.044 & 0.247
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
is also plotted.  Our model predictions provide a significantly better match to the data.

In the fit to our model, the observed color excess is attributed to   extrinsic
%----
$E_\gamma(B-V)=  0.93 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.27 \pm   0.08$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
\color{red}
objects with the extreme median values have 
%---
$E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$ 
%---
\color{black}
(see Figure~\ref{ebv:fig}).
\textcolor{red}{The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span} of supernovae used to train the coefficients of the model.

>>>>

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the infrequent selection of supernovae
heavily extinguished by host-galaxy dust.
Outliers  are also clearly distinguished in  $EW_{Ca}$--$\lambda_{Si}$ space.

@@

\subsection{Two Extrinsic Parameters $k_0$ and $k_1$}
\color{red}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
\color{black}
None of the 20000 links of 
our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k_0$ and $k_1$  on supernova magnitudes
with probability $(1-5\times 10^{-5})$.

\color{red}
Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
estimate $R_V=A_V/(E(B-V)-zeropoint)$ per supernova, shown in Figure~\ref{avebv:fig}.
Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.52 \pm   0.08$, indicating that different physics
operate in these regimes.

@@

Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
parameters of a single  dust model.  Indeed the \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\end{equation}
The \citet{1999PASP..111...63F} model is also approximately described by a linear model in the range of $R_V$ and wavelength under consideration:
the results to follow vary at the percent level when making this approximation.
Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
\end{equation}

For the linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.15 & 2.82 \\
0.75 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to a constant:  these are shown in Figure~\ref{avebv:fig}.
The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
The linear fit also produces the zeropoint, allowing us to determine $R^F_V$ for each supernova,
which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
    \caption{\textcolor{red}{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
onto the Fitzpatrick plane.  Right: $R^F_V$ for each supernova.}
   \label{avebv_synth:fig}}
\end{figure}

The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
external dust is responsible for most of our $k_0$ and $k_1$ parameters.

@@

\subsection{SN 2014J in the Context of Our Model}
\label{sn2014j:sec}

Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
These data are fit to the model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)k_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)k_1,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.

The best-fit parameters for SN~2014J are 
%----
$k_0= 2.65$, $ k_1=-1.64$ with covariance
%----
\begin{equation}
\begin{pmatrix}
0.048 & 0.047 \\
0.047 & 0.248
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
is also plotted.  Our model predictions provide a significantly better match to the data.

In the fit to our model, the observed color excess is attributed to   extrinsic
%----
$E_{\gamma^0}(B-V)=  0.92 \pm   0.08$ and intrinsic $E_{\gamma_1}(B-V)=  0.28 \pm   0.08$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\gamma^0$ and $\gamma^1$, the
\color{red}
objects with the extreme median values have 
%---
$E_{\gamma^0}(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
and for $E_{\gamma^1}(B-V)$ $-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$ 
%---
(see Figure~\ref{ebv:fig}).
The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span of supernovae used to train the coefficients of the model, which is not unexpected if
attributed to dust.

\section{Intrinsic Color}
\label{model2:sec}
Analysis of the data using the model presented in \S\ref{model:sec} drew out parameter values consistent
with two-parameter dust models.  We now consider an extension to the model that accommodate an additional
color parameter.
The new model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$ to the absolute magnitudes.
Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes through $\delta$. 
Although
this term is introduced through the absolute rather than observed magnitude,
practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
degeneracy, for convenience we refer to this term as ``intrinsic''.

To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
\end{equation}
The first specifies the definition of zero color.   The latter two confine possible magnitude
variations to those unattributablabe to 
the $\gamma k$ terms (i.e.\ dust); without this pragmatic condition $\delta D$  
was degenerate and tended toward $\gamma k$ in the fit.  The initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.

The resulting posteriors of our parameters are given in Table~\ref{}
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters \label{global2:tab}}
\end{table}

For dust and our model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
It turns out that the planes for both models are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.16 & 2.82 \\
0.74 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

@@
